Output Summary

### 2020-12-16 03-post-process/output-plots.Rmd
Add new parameters to diagnostics in output plots

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  scenario:
    label: "Scenario"
    value: base
    input: text
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "gamma",
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
)

@@

>>>>

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  scenario:
    label: "Scenario"
    value: "relate-hat-nat"
    input: text
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "gamma",
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
  "^phi_M_O1", "^phi_O1_O2", "^phi_O2_O3",
  "^psi_O1_Rb", "^psi_O2_Rb", "surv_scaler"
)

@@

`r if (params$mcmc_plots) "### surv_scaler"`

```{r surv-scaler-diag-plots, eval = params$mcmc_plots, fig.width = 5, fig.height = 7}
diag_plots(post, "surv_scaler", layout = "4x1")
```
